Search-Based Test Data Generation for JavaScript Functions with DOM

### 2018-01-04 doc/icse2018/icse2018.tex
Working on introduction.

\section{Introduction}
\label{sec.intro}
Recent empirical study of client-side JavaScript bugs~\cite{frolin:TSE16} has shown that 68\% of faults are DOM related.

>>>>

\section{Introduction}
\label{sec.intro}

According to the Stack Overflow survey\footnote{\url{https://insights.stackoverflow.com/survey/2017}} run in 2017 across developers, JavaScript has been recognized for the firth time in row as the most commonly used programming language with Node.js as the most commonly used technology. Such a tremendous ever increasing success of JS happens thanks to various language features including dynamic typing, native browser support (DOM).

Say about popularity of JS applications including nodejs. Cite some works referring to challenges in testing.

Common mistakes JS developers do\footnote{\url{https://www.toptal.com/javascript/10-most-common-javascript-mistakes}}.

Notable errors in 2017\footnote{\url{https://www.fastcompany.com/40505226/the-year-that-software-bugs-ate-the-world}}.

List current practices in testing and show where they fail. Make connection with DOM.

The state of JS 2017 survey~\footnote{\url{https://stateofjs.com/}} contains an extensive list of testing frameworks including Mocha, Jasmine, Jest, Enzyme, Tape, Ava, Karma and QUnit among the most used ones in the decreasing order of popularity. These frameworks support testing at different levels unit, integration and functional. The same survey also indicated relatively low satisfaction rate of the current state of JS testing tools, only 3.2 out of 5. As result, new testing frameworks such as Cypress and Storybook are constantly appearing to improve the situation. But despite of this effort, test data generation stays a missing component not being properly addressed by any of the widely used testing frameworks. Research community has actively been working towards making progress in this direction introducing such tools as Artemis~\cite{artemis2011}, JSConTest~\cite{heidegger2010contract}, Crawljax~\cite{mesbah2012crawling}, JSeft~\cite{mirshokraie2015jseft} and Jalangi~\cite{sen2013jalangi}.

Recent study of client-side JS bugs~\cite{ocariza2017study} has shown that majority (68\%) of JS faults are DOM-related and occur in the JS code itself. This fact indicates that a better

Introduce search-based test generation.

Recent empirical study of client-side JavaScript bugs~\cite{frolin:TSE16} has shown that 68\% of faults are DOM related.
